\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Refactoring variables
Added more words

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$F_B(s)$] the probability curve for differences in travel time within B
    \item[$T_{A+}$] average travel time in the direction of B to A inside of A
    \item[$T_{A-}$] average travel time in the direction of A to B inside of A
    \item[$T_{B+}$] average travel time in the direction of A to B inside of B
    \item[$T_{B-}$] average travel time in the direction of B to A inside of B
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out

the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal

>>>>

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$F_B(s)$] the probability curve for differences in travel time within B
    \item[$T_A$] average travel time inside of A
    \item[$T_{A+}$] average travel time in the direction of B to A inside of A
    \item[$T_{A-}$] average travel time in the direction of A to B inside of A
    \item[$T_B$] average travel time inside of B
    \item[$T_{B+}$] average travel time in the direction of A to B inside of B
    \item[$T_{B-}$] average travel time in the direction of B to A inside of B
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$
